{\cis}: A Python Package for Integrating Computational Models Across Languages and Scales

### 2018-10-11 papers/lang2018/ms.tex
Add moore grant to acknowledgements

%---------------------------------------------------------------------------------
% ACKNOWLEDGMENTS
\section*{Acknowledgments}
\ifieee
\else
\acknowledgments
\fi
%
This work was supported by funding from the Foundation for Food and Agriculture Research (FFAR), Institute for Sustainability, Energy, and Environment (iSEE), and the National Center for Supercomputing Applications (NCSA).
The authors would like to thank Mike Lambert and Craig Willis for their ongoing work on a graphical user interface for visually composing and running integration networks for {\cis} as well as David Raila for his work on the original integration code that {\cis} was based on.

>>>>

%---------------------------------------------------------------------------------
% ACKNOWLEDGMENTS
\section*{Acknowledgments}
\ifieee
\else
\acknowledgments
\fi
%
This work was supported by funding from the Foundation for Food and Agriculture Research (FFAR), Institute for Sustainability, Energy, and Environment (iSEE), the National Center for Supercomputing Applications (NCSA), and the Gordon and Betty Moore Foundation's Data-Driven Discovery Initiative through Grant GBMF4561 to Matthew Turk. 
%
The authors would like to thank Mike Lambert and Craig Willis for their ongoing work on a graphical user interface for visually composing and running integration networks for {\cis} as well as David Raila for his work on the original integration code that {\cis} was based on.
